Hyperplane Elimination for Quickly Enumerating Local Optima

### 2015-09-09 Hyperplane Enumeration/main.tex
Changed up sections, more figures

\section{Finding Local Optima}
TODO Concatenated Traps using $N>40$ has slope of 2.
\begin{figure*}
  \centering
  \includegraphicsfit{length-method}
  \caption{Comparison of how each method scales with problem size on log-linear scales. Each point is the mean
           runtime over 30 instances and each line the linear model. All confidence intervals too tight to see.}
  \label{fig-length-method}
\end{figure*}

@@

\section{Finding $r$-Bit Local Optima}

\section{Examining Local Optima}

>>>>

\section{Experiments}
TODO Explain experimental setup details here.

\subsection{Finding Local Optima}
TODO Concatenated Traps using $N>40$ has slope of 2.
\begin{figure*}
  \centering
  \includegraphicsfit{length-method}
  \caption{Comparison of how each method scales with problem size on log-linear scales. Each point is the mean
           runtime over 30 instances and each line the linear model. All confidence intervals too tight to see.}
  \label{fig-length-method}
\end{figure*}

@@

\subsection{Finding $r$-Bit Local Optima}

\begin{figure*}
  \centering
  \includegraphicsfit{slope-method}
  \caption{Estimated slope with 95\% confidence intervals for each method to find $r$-bit local optima. Slope is $m$ in the model $y = 2^c2^{mN}$
           where $y$ is number of seconds required to
	         find all local optima of a problem using $N$ bits.}
  \label{fig-boxplot-method}
\end{figure*}

\subsection{Examining Local Optima}

\begin{figure*}
  \centering
  \includegraphicsfit{length-radius}
  \caption{Number of $r$-bit local optima as $N$ increases for each problem.}
  \label{fig-boxplot-method}
\end{figure*}
